Report on a Safety Checker for Petri nets

### 2013-11-18 paper/workspace/main.tex
Updated main.
Updated paper

* State constraints C:

@@

\newpage
\begin{verbatim}
* Dual state constraints C':

@@

  target1 >= 0
  nc      >= 0
  m       >= 0
  cs1     >= target1
  cs2     >= target1
\end{verbatim}

\begin{verbatim}
* Model A:

@@

* Invariant:

@@

\begin{verbatim}
* State constraints C:

  nc  =  2 - t1 - t2 + t3 + t4
  m1  =  1 - t1 + t3
  m2  =  1 - t2 + t4
  cs1 =  0 + t1 - t3
  cs2 =  0 + t2 - t4

  nc  >= 0
  m1  >= 0
  m2  >= 0
  cs1 >= 0
  cs2 >= 0
  t1  >= 0
  t2  >= 0
  t3  >= 0
  t4  >= 0

* Assignment A:
  nc  = 0
  m1  = 0
  m2  = 0
  cs1 = 1
  cs2 = 1
  t1  = 1
  t2  = 1
  t3  = 0
  t4  = 0

* Trap conditions C_\theta:
  nc  => t1 /\ t2
  m1  => t1 /\ t2
  m2  => t1 /\ t2
  cs1 => t3
  cs2 => t4

@@

* Assignment A_\theta:
  nc  = false
  m1  = true
  m2  = true
  cs1 = false
  cs2 = false

@@

* Constraint \delta:
  m1 + m2 >= 1
\end{verbatim}

@@

\newpage

\section{Benchmarks of \mist}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 14 benchmarks in Appendix~\ref{mist-experiments-c1} are positive.
\item Composing state constraints with TrapConditions gives the following 6 additional positives.
\begin{verbatim}
PN/pingpong
PN/basicME
PN/multiME
boundedPN/lamport
boundedPN/newdekker
boundedPN/peterson
\end{verbatim}
\item Composing state constraints with TrapConditions and SubnetTrapConditions gives the additional positive \ttt{PN/manufacturing}.
  \item The remaining positive benchmarks are the following.
\begin{verbatim}
PN/extendedread-write
PN/extendedread-write-smallconsts
\end{verbatim}
\end{itemize}
\end{document}

>>>>

* Example:
  - State constraints C:

@@

\newpage
\begin{verbatim}
* Example:
  - Dual state constraints C':

@@

    target1 >= 0
    nc      >= 0
    m       >= 0
    cs1     >= target1
    cs2     >= target1

  - Model A:

@@

  - Invariant:

@@

\newpage
\begin{verbatim}
* Example
  - State constraints C:
    nc  =  2 - t1 - t2 + t3 + t4
    m1  =  1 - t1 + t3
    m2  =  1 - t2 + t4
    cs1 =  0 + t1 - t3
    cs2 =  0 + t2 - t4
    nc  >= 0
    m1  >= 0
    m2  >= 0
    cs1 >= 0
    cs2 >= 0
    t1  >= 0
    t2  >= 0
    t3  >= 0
    t4  >= 0

  - Assignment A:
    nc  = 0
    m1  = 0
    m2  = 0
    cs1 = 1
    cs2 = 1
    t1  = 1
    t2  = 1
    t3  = 0
    t4  = 0

  - Trap conditions C_\theta:
    nc  => t1 /\ t2
    m1  => t1 /\ t2
    m2  => t1 /\ t2
    cs1 => t3
    cs2 => t4

@@

  - Assignment A_\theta:
    nc  = false
    m1  = true
    m2  = true
    cs1 = false
    cs2 = false

@@

  - Constraint \delta:
    m1 + m2 >= 1
\end{verbatim}

\newpage
\section{Benchmarks of \mist}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 14 benchmarks in Appendix~\ref{mist-experiments-c1} are positive.
\item Composing state constraints with TrapConditions gives the following 6 additional positives.
\begin{verbatim}
PN/pingpong
PN/basicME
PN/multiME
boundedPN/lamport
boundedPN/newdekker
boundedPN/peterson
\end{verbatim}
\item Composing state constraints with TrapConditions and SubnetTrapConditions gives the additional positive \ttt{PN/manufacturing}.
  \item The remaining positive benchmarks are the following.
\begin{verbatim}
PN/extendedread-write
PN/extendedread-write-smallconsts
\end{verbatim}
\end{itemize}

@@

\end{document}
